---
title: "Wrangling Data"
author: "Brandi Pessman"
date: "2024-12-10"
output: html_document
---

# Load Libraries

```{r libraries}
library(tidyverse)
library(lubridate)
```

# Import Data

```{r import}
prey_import <- read.csv("data/prey_capture_2021.csv") %>% 
  # only females that survived and no silent treatments
  filter(sex == "F",
         died_yn == "n",
         treatment1 == "loud" | treatment1 == "quiet",
         treatment2 == "loud" | treatment2 == "quiet") 

spider_measurements <- read.csv("data/spider_measurements.csv", header = TRUE) %>% 
  filter(body_part == "carapace_w") %>% 
  dplyr::select(-angle, -measure) 

web <- read.csv("data/web_pictures.csv", header = TRUE) %>% 
  filter(Week < 4) %>% 
  mutate(site = fct_recode(noise_location, "Rural" = "rural", "Urban" = "city"),
         corrected = pic_mean / black_mean) %>% 
  dplyr::select(spider, site, Week, pic_mean, corrected, StdDev)

mating_import <- read.csv("data/mating_2022.csv") 

learning_import <- read.csv("data/learning_scc.csv", header = TRUE)
```

# Prey Capture

```{r spider condition}
prey_cond <- prey_import %>% 
  dplyr::select(spider, mass_mg)

prey_cond <- left_join(prey_cond, spider_measurements, by = "spider")
rownames(prey_cond) <- c(prey_cond$spider)
cond <- data.frame(cbind(condition = residuals(lm(log(mass_mg) ~ log(length), data = prey_cond)),
                         spider = names(residuals(lm(log(mass_mg) ~ log(length), data = prey_cond)))))
prey_cond <- full_join(prey_cond, cond, by = "spider") %>% 
  mutate(condition = as.numeric(condition)) %>% 
  dplyr::select(spider, condition)
```

```{r prey capture}
prey_main <- prey_import %>% 
  # treatment and noise location factor wrangling
  mutate(treatment1 = fct_recode(treatment1, "Loud" = "loud", "Quiet" = "quiet"),
         treatment2 = fct_recode(treatment2, "Loud" = "loud", "Quiet" = "quiet"),
         treatment1 = fct_relevel(treatment1, "Quiet", "Loud"),
         treatment2 = fct_relevel(treatment2, "Quiet", "Loud"),
         site = fct_recode(noise_location, "Urban" = "city", "Rural" = "rural"),
         site = fct_relevel(factor(site), "Rural", "Urban")) %>% 
  unite("site_t1", c(site, treatment1), sep = "_", remove = FALSE) %>% 
  unite("t1_t2", c(treatment1, treatment2), sep = "_", remove = FALSE) %>% 
  mutate(site_t1 = fct_relevel(factor(site_t1), "Rural_Quiet", "Urban_Quiet", "Rural_Loud", "Urban_Loud"),
         t1_t2 = fct_relevel(factor(t1_t2), "Quiet_Quiet", "Quiet_Loud", "Loud_Quiet", "Loud_Loud")) %>% 
  # age and timing wrangling
  # age at beginning of experiment
  mutate(age = ifelse(line_date1 == "9/4/21", as.numeric(mdy("09/04/21") - mdy(lastmolt)),
                      as.numeric(mdy("09/05/21") - mdy(lastmolt))), 
         lastmolt = mdy(lastmolt),
         date_collected = mdy(date_collected),
         # juvenile time in lab
         lab2mature = as.numeric(lastmolt - date_collected), 
         # time in spider room
         lab2silence = as.numeric(mdy(date_added) - date_collected),
         field_attack_time = ifelse(vibr_sec == "no reaction", 30, as.numeric(vibr_sec)),
         field_attack_time_ms = field_attack_time * 1000) 

prey_main <- left_join(prey_main, prey_cond, by = "spider")

prey_main <- prey_main %>%
  # pivoting and reformatting (remove trial 1, completed on 'silent' web)
  dplyr::select(spider, mass_mg, condition, age, field_attack_time, field_attack_time_ms, date_collected, lastmolt, lab2mature, lab2silence, site, treatment1, treatment2, site_t1, t1_t2, silk_mass_bs, tb_2, tb_3, tb_4, tb_5, tb_6, tb_7, tb_8, tb_9, tb_10, tb_11, tb_12, prey_2, prey_3, prey_4, prey_5, prey_6, prey_7, prey_8, prey_9, prey_10, prey_11, prey_12) %>% 
  pivot_longer(cols = c(tb_2:prey_12), names_to = "stimulus_trial", values_to = "attack_time") %>% 
  separate(col = stimulus_trial, into = c("stimulus", "trial"), sep = "_") %>%
  mutate(stimulus = fct_recode(stimulus, "Artificial" = "tb", "Live" = "prey"),
         trial = as.numeric(trial) - 1,
         spider = factor(spider),
         # give a 1 or 0 by whether or not they attacked in 30 s 
         attack = ifelse(attack_time == 30, 0, 1),
         attack_time_ms = attack_time * 1000,
         web_treatment = ifelse(trial <= 5, "web1_t1", 
                                ifelse(trial == 6, "web1_t2", "web2_t2")),
         treatment = factor(ifelse(trial < 6, paste0(treatment1, "1"), paste0(treatment2, "2"))),
         #treatment = ifelse(treatment == 1, "Quiet1", "Quiet2", "Loud"),
         treatment = fct_relevel(treatment, "Quiet1", "Quiet2", "Loud1", "Loud2")) %>% 
  dplyr::select(spider, mass_mg, condition, age, field_attack_time, field_attack_time_ms, date_collected, lastmolt, lab2mature, lab2silence, silk_mass_bs, site, treatment1, treatment2, site_t1, t1_t2, web_treatment, treatment, trial, stimulus, attack, attack_time, attack_time_ms)
```

```{r spider_df}
spider_df <- prey_main %>% 
  dplyr::select(spider, age, mass_mg, condition, field_attack_time, field_attack_time_ms, date_collected, lastmolt, lab2mature, lab2silence, site, treatment1, treatment2, site_t1, t1_t2, silk_mass_bs) %>%
  mutate(field_attack = ifelse(field_attack_time == 30, 0, 1)) %>% 
  unique()

web <- left_join(spider_df, web, by = c("spider", "site")) %>% 
  mutate(silk_per_body = silk_mass_bs / (mass_mg / 1000))
```

```{r rapid noise change}
before_avg <- prey_main %>% 
  filter(stimulus == "Artificial",
         attack == 1,
         trial < 6) %>% 
  dplyr::select(-attack) %>% 
  group_by(spider, site, site_t1, treatment1, treatment2, t1_t2) %>% 
  summarize(attack_time = mean(attack_time),
            attack_time_ms = floor(attack_time * 1000), # removes decimals which don't work for glm.nb
            trial = "Before")

switch <- prey_main %>% 
  filter(stimulus == "Artificial", 
         trial == 6,
         attack == 1) %>% 
  dplyr::select(spider, site, site_t1, treatment1, treatment2, t1_t2, attack_time, attack_time_ms) %>%
  mutate(trial = "After") 


switch <- rbind(switch, before_avg) %>% 
  mutate(treatment1 = as.character(treatment1),
         treatment2 = as.character(treatment2),
         treatment = ifelse(trial == "Before", treatment1, treatment2),
         treatment = fct_relevel(factor(treatment), "Quiet", "Loud"),
         treatment1 = factor(treatment1),
         treatment2 = factor(treatment2),
         treatment1 = fct_relevel(factor(treatment1), "Quiet", "Loud"),
         treatment2 = fct_relevel(factor(treatment2), "Quiet", "Loud"),
         t1_t2_abb = fct_recode(factor(t1_t2), "L-L" = "Loud_Loud", "Q-Q" = "Quiet_Quiet", "L-Q" = "Loud_Quiet", "Q-L" = "Quiet_Loud"),
         t1_t2_abb = fct_relevel(factor(t1_t2_abb), "Q-Q", "L-L", "L-Q", "Q-L"))
```

# Mating

Number of Bobs
- bobs_before_quiescent = bob # from start to quiescent
- bobs_before = bob # from start to copulation
- bobs_quiescent = bob # from start of quiescent to copulation
- bobs_mating1 = bob # during first copulation
- bobs_after = bob # from after the end of the first copulation bout

Number of Bouts
- quiescent_bouts = number of times females entered quiescence during the first copulation bout (?)
- num_matings = number of copulation bouts

**TIMING**
Before Quiescence 
- quiescent_lat_s = seconds from first bob (?) to quiescence

Pre-Copulation Quiescence 
- quiescent_mate = seconds from the start of quiescence to the start of copulation

During Copulation 
- total_quiescent1 = seconds female was quiescent during the first copulation (from the beginning of quiescence or beginning of copulation?)
- remains_quiescent = Y or N whether female ever wakes during first (?) copulation
- total_mating1 = seconds from start to end of first copulation bout
- total_mating2 = seconds from start to end of second copulation bout
- total_mating3 = seconds from start to end of third copulation bout
- partial_mating = seconds of copulation for trial where video recording was interupted (start of copulation bout to video end)
- total_mating = sum of total_mating1, 2, and 3 and partial

Pre-Copulation + Copulation Length
- mating_lat_s = seconds from first bob (?) to copulation

Video Length
- total_video = seconds of video length

```{r mating}
mating <- mating_import %>% 
  mutate(F_age = as.numeric(mdy(Mate_Date) - mdy(F_mature)),
         M_age = as.numeric(mdy(Mate_Date) - mdy(M_mature)),
         age_diff = abs(F_age - M_age),
         mass_diff = abs(F_mass_mg - M_mass_mg),
         Treatment = fct_relevel(Treatment, "Quiet", "Loud"),
         Site = fct_relevel(Site, "Rural", "Urban")) %>% 
  filter(! is.na(F_age)) %>% 
  unite("site_treatment", c(Site, Treatment), sep = "_", remove = FALSE)

rownames(mating) <- c(mating$F_ID)
cond_f <- data.frame(cbind(F_condition = residuals(lm(log(F_mass_mg) ~ log(F_ceph_width_mm), 
                                                      data = mating)), 
                           F_ID = names(residuals(lm(log(F_mass_mg) ~ log(F_ceph_width_mm), 
                                                     data = mating)))))
# add condition to the dataset
mating <- full_join(mating, cond_f, by = "F_ID") %>% 
  mutate(F_condition = as.numeric(F_condition))

rownames(mating) <- c(mating$M_ID)
cond_m <- data.frame(cbind(M_condition = residuals(lm(log(M_mass_mg) ~ log(M_ceph_width_mm),
                                                      data = mating)),
                           M_ID = names(residuals(lm(log(M_mass_mg) ~ log(M_ceph_width_mm), 
                                                     data = mating)))))
# add condition to the dataset
mating <- full_join(mating, cond_m, by = "M_ID") %>% 
  mutate(M_condition = as.numeric(M_condition))

mating <- mating %>% 
  mutate(cond_diff = abs(F_condition - M_condition),
         # whether the female woke at any point before or during the first copulation bout
         quiescent_interuption = ifelse(quiescent_bouts > 1, 1, 0),
         # whether the female remained quiescent after copulation ended
         remains_quiescent = ifelse(remains_quiescent == "Y", 1, 0),
         bob_rate_before_quiescent = bobs_before_quiescent / (quiescent_lat_s / 60),
         bobs_quiescent = bobs_before - bobs_before_quiescent,
         bob_rate_quiescent = bobs_quiescent / (quiescent_mate / 60),
         bob_rate_mating1 = bobs_mating1 / (total_mating1 / 60),
         more_bobs_before_cop = ifelse(bobs_before > bobs_mating1, 1, 0)) %>% 
  dplyr::select(F_ID, F_age, F_condition, M_ID, M_age, M_condition, age_diff, cond_diff, Site, Treatment, site_treatment, Mate_Date, Mated, 
                bobs_before_quiescent, bobs_quiescent, bobs_mating1, 
                bob_rate_before_quiescent, bob_rate_quiescent, bob_rate_mating1,
                quiescent_lat_s, quiescent_mate, total_mating1, quiescent_interuption, remains_quiescent, total_video, num_matings)
```

# Container Levels

```{r container levels}
datapath = "/Users/bjpessman/Documents/phd_research_code/Prey_Capture/playback_tests"
setwd(datapath)
txt_files_ls = list.files(path = datapath, pattern = "*.txt")
txt_files_df <- lapply(txt_files_ls,
                       function(x){
                         read.table(file = x, header = TRUE, sep ="\t")
                         })
for (i in 1:length(txt_files_df)){
  txt_files_df[[i]] <- cbind(txt_files_df[[i]],txt_files_ls[i])
  }
main <- do.call("rbind", lapply(txt_files_df, as.data.frame))
main <- main %>%
  dplyr::select(Low.Freq..Hz., Inband.Power..dB.FS., `txt_files_ls[i]`)
colnames(main) <- c("Low_Freq", "Power", "File")
main <- main %>%
  separate_wider_delim(cols = File, names = c("Name", "Ext"), ".") %>%
  separate_wider_delim(cols = Name, names = c("Tub", "Container", "Position", "Treatment"), "_") %>%
  separate(col = Tub, into = c("Label_Tub", "Tub"), sep = -1) %>%
  separate(col = Container, into = c("Label_Cont", "Container"), sep = -1) %>%
  dplyr::select(Treatment, Position, Tub, Container, Low_Freq, Power) %>% 
  unite(Tub_Cont, c(Tub, Container), sep = "_", remove = FALSE) %>% 
  filter(Low_Freq < 1000,
         Position == "bottom") %>% 
  mutate(Treatment = factor(Treatment),
         Treatment = fct_recode(Treatment, "Loud" = "loud", "Quiet" = "quiet", "Silent" = "silent"),
         Treatment = fct_relevel(Treatment, "Silent", "Quiet", "Loud"))

silent <- main %>% 
  filter(Treatment == "Silent",
         #Tub_Cont == "1_3"
         ) %>% 
  mutate(Power_silent_dB = Power,
         snr_silent_u = 10^(Power_silent_dB/10),
         snr_silent_dB = 10 * log10(snr_silent_u)) %>% 
  group_by(Low_Freq) %>% 
  summarize(snr_silent_dB_avg = mean(snr_silent_dB))
  #dplyr::select(Low_Freq, Power_silent) 

playback <- main %>% 
  filter(! Treatment == "Silent") %>% 
  mutate(Power_playback = Power) %>% 
  dplyr::select(-Power) 

playback <- full_join(playback, silent, by = "Low_Freq") %>% 
  mutate(Power = Power_playback - snr_silent_dB_avg)
```

# Learning with SCC Animal Behavior Class

```{r learning}
learning_sum1 <- learning_import %>% 
  dplyr::select(SpiderID, Site, Treatment, Eggs2, Cond_Attack_1, Avg_Test) %>% 
  pivot_longer(cols = c(Cond_Attack_1, Avg_Test), names_to = "Measure", values_to = "TimeToAttack") %>% 
  mutate(Measure = fct_recode(Measure, "Conditioning1" = "Cond_Attack_1", "TestingAvg" = "Avg_Test"))


learning_sum2 <- learning_import %>% 
  dplyr::select(SpiderID, Site, Treatment, Eggs2, Attacked_1, Attacked_Test) %>% 
  pivot_longer(cols = c(Attacked_1, Attacked_Test), names_to = "Measure", values_to = "Attacked") %>% 
  mutate(Measure = fct_recode(Measure, "Conditioning1" = "Attacked_1", "TestingAvg" = "Attacked_Test"),
         Attacked = ifelse(Attacked == "Y", 1, 0))

learning <- full_join(learning_sum1, learning_sum2, by = c("SpiderID", "Site","Treatment", "Eggs2", "Measure"))
```

# Save RDS 

```{r save}
saveRDS(prey_main, "wrangled_data/prey_main.rds")
saveRDS(spider_df, "wrangled_data/spider_df.rds")
saveRDS(switch, "wrangled_data/switch.rds")
saveRDS(web, "wrangled_data/web.rds")
saveRDS(mating, "wrangled_data/mating.rds")
saveRDS(playback, "wrangled_data/playback.rds")
saveRDS(learning, "wrangled_data/learning.rds")
```